worldmap

### 2024-11-12 analysis/figures/visualization.Rmd
Export legends for each of the colors, save out with better aspect ratio

slopes <- model_output %>% 
  filter(term == "year_scaled", model_id == "base",
         !metric %in% c("FDiv", "FRic", "FEve", "Jaccard_next")) %>% 
  select(metric, estimate, p.adjust, study_id) %>%
  group_by(metric) %>%
  #rowwise() %>%
  mutate(across(estimate, ~scale(.)[,1])) %>%
  ungroup() %>%
    mutate(ind = case_when(
    estimate > 0 & p.adjust < 0.05 ~ "blue", 
    estimate < 0 & p.adjust < 0.05 ~ "red", 
    .default = "grey"
  )) %>%
  left_join(durations) %>%
  mutate(duration = as.factor(duration))

@@

  metric_plot <- plot_data %>% 
    filter(!is.na(study_id)) %>% 
    ggplot() +
    geom_dotplot(aes(x = estimate, fill = duration), 
                 #stackdir = "center",
                 stackgroups = TRUE,
                 method = "histodot", 
                 binwidth = 0.15, dotsize = 1.15
    ) +
    scale_fill_manual(values = graid_pal, guide = "none", drop = FALSE) +
    geom_vline(aes(xintercept = gen_est$estimate), linetype = "longdash") +
    theme_minimal() +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          axis.title.y = element_blank(), 
          axis.text.y=element_blank(), 
          axis.title=element_text(size=14,face="bold")) +
    #labs(title = plot_label) +
    xlim(-3.15, 3.15) +
    #ylim(0, 2.5) +
    annotate('text', x = -2.5, y = 0.8, label = plot_label, size = unit(7, "pt"))

@@

duration_legend_plot <- slopes %>%
  ggplot(aes(y = metric, x = estimate, color = duration)) +
  geom_point() +
  scale_color_gradient(low = "white", high = "#77976e")

duration_legend <- get_legend(duration_legend_plot)

test_plot <- slope_plot_grid + draw_grob(duration_legend,  .8, -.2, .3/3.3, 1, scale = 5)

cowplot::save_plot(here::here("figures/slope_plot_grid.png"), slope_plot_grid, ncol = 7, nrow = 5, bg = "white", base_asp = 1.18)
# plot_grid(plotlist=slope_plots, labels = "AUTO", nrow = 3, align = 'vh',
#                        hjust = -1, axis = "l", scale = 0.9)
```

>>>>

slopes <- model_output %>% 
  filter(term == "year_scaled", model_id == "base",
         !metric %in% c("FDiv", "FRic", "FEve", "Jaccard_next")) %>% 
  select(metric, estimate, p.adjust, study_id) %>%
  group_by(metric) %>%
  #rowwise() %>%
  mutate(across(estimate, ~scale(.)[,1])) %>%
  ungroup() %>%
    mutate(ind = case_when(
    estimate > 0 & p.adjust < 0.05 ~ "blue", 
    estimate < 0 & p.adjust < 0.05 ~ "red", 
    .default = "grey"
  )) %>%
  left_join(durations) %>%
  mutate(duration_fac = as.factor(duration))

@@

  metric_plot <- plot_data %>% 
    filter(!is.na(study_id)) %>% 
    ggplot() +
    geom_dotplot(aes(x = estimate, fill = duration_fac), 
                 stackgroups = TRUE,
                 method = "histodot", 
                 binwidth = 0.15, dotsize = 1.15
    ) +
    scale_fill_manual(values = graid_pal, guide = "none", drop = FALSE) +
    geom_vline(aes(xintercept = gen_est$estimate), linetype = "longdash") +
    theme_minimal() +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          axis.title.y = element_blank(), 
          axis.text.y=element_blank(), 
          axis.title=element_text(size=14)) ++
    xlim(-3.15, 3.15) +
    xlab("temporal trend") +
    annotate('text', x = -2.5, y = 0.8, label = plot_label, size = unit(7, "pt"))

@@

cowplot::save_plot(here::here("figures/slope_plot_grid.png"), slope_plot_grid, ncol = 7, nrow = 5, bg = "white", base_asp = 1.18)

get_legends <- function(color){
  duration_legend_plot <- slopes %>%
    ggplot(aes(y = metric, x = estimate, color = duration)) +
    geom_point() +
    scale_color_gradient(low = "white", high = color) +
    theme(legend.title = element_blank(), legend.text = element_blank(), 
          legend.background = element_rect(fill='transparent'))

  duration_legend <- get_legend(duration_legend_plot)
  leg <- grid.arrange(duration_legend)
  ggsave(here::here(paste0("figures/slope_legends/", color, "_legend.png")), leg, width = .6, height = 1.5,
         bg = "transparent")
}

map(muted, get_legends)

```
